Electric polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2018-12-16 SI.tex
Changes adapted from Elton 20181212

\usepackage{xr}
\externaldocument[main-]{paper}

@@

\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
\begin{document}

\newpage{}
\section{Further Analysis of the 2D Polarizability Model}
\label{sec:2D-pol}

In this section, we discuss further topics about the 2D polarizability
model proposed in the main text.

\subsection{Profile of induced dipoles of 2D material}
\label{sec:dipole-plot}
Here we show in detail the
$\Delta \rho=\rho(\boldsymbol{E}) - \rho(\boldsymbol{E}=0)$ profile of
the 2H-MoS$_{2}$ slab in main text Figure \ref{main-fig-1}a. The
density $\rho$ is calculated as the average value in the
\textit{xy}-plane, and the value is shown in Figure
\ref{fig:rho-profile}. As can be seen the induced charges on the
MoS$_{2}$ layer only extends to a width of $\sim{}$12 \AA{}. When the
SL size $L \gg$12 \AA{} as in the first principle calculations done in
the main text, the induced dipoles from the periodic images do not
interact, and thus giving converged values of $\alpha_{\mathrm{2D}}$.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/SI-dipole-MoS2.pdf}
  \caption{Induced dipole profile of a 2H-MoS$_{2}$ slab inside the
    superlattice, corresponding to main text Figure
    \ref{main-fig-1}a. \textbf{a}. Scheme of the MoS$_{2}$ layer
    inside the SL separated by vacuum layer. The dielectric constant
    $\varepsilon_{\mathrm{SL}}$ is combined effect of the 2D
    polarizability $\alpha_{\mathrm{2D}}$ and the vacuum
    layer. \textbf{b}. $\Delta \rho$ as a function of $z$ around the
    MoS$_{2}$ layer, green and red parts corresponding to negative and
    positive induced charges. The external electric field
    $E_{\mathrm{ext}}$ is 0.01 eV/\AA{}.}
  \label{fig:rho-profile}
\end{figure}

\subsection{Hypothetical 2D ``dielectric constant'' rescaled from 3D dielectric constant}
\label{sec:2D-3D-rescale}
From literatures, it is often desired to extract the ``dielectric
constant'' of a 2D material from the 3D macroscopic dielectric
constant of the superlattice, where the layers are periodic along of
x,y directions but separated by a vacuum layer between its images
\cite{Matthes_2016,Laturia_2018}. As discussed in the main text, the
definition of the 2D ``dielectric constant'' (in particular, its
in-plane components) is questionable, due to the locality of
electrostatic screening of the 2D materials
\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Here we show
that, in addition to the ambiguous definition of the 2D dielectric
constant, such approach requires the precise determination of the 2D
layer thickness $\delta_{\mathrm{2D}}$, which makes it impractical.

@@

\begin{eqnarray}
  \label{eq:MG-effect-1}
  &\varepsilon_{\mathrm{SL}}^{\parallel} &= f \varepsilon_{\mathrm{2D}}^{\parallel} + (1 - f)\\
  \label{eq:MG-effect-2}
  &(\varepsilon_{\mathrm{SL}}^{\perp})^{-1} &= f /\varepsilon_{\mathrm{2D}}^{\perp} + (1-f)
\end{eqnarray}
where $f=\delta/L$ is the volume fraction of the 2D
material in the superlattice. The major issue when using such rescale
relations comes from the determination of $\delta_{\mathrm{2D}}$. To
eliminate the modeling error caused by the \textit{a priori} parameter
selection of $\delta$, we perform the calculation of
$\varepsilon_{\mathrm{SL}}$ of group 6 TMDCs against different $L$,
and use least-square fitting to extract both
$\varepsilon$ and $\delta$, as shown in
Figure \ref{fig:rescale-prb}.

@@

\subsection{Dependence of $\alpha_{\mathrm{2D}}$ on bandgap}
\label{sec:pol-2D-Eg}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\linewidth]{img/SI-compare_alpha_Eg.pdf}
  \caption{Relation between $1/\alpha_{\mathrm{2D}}^{\parallel}$ and various choices
    of $E_{\mathrm{g}}$: minimal gap from HSE06 (blue), minimal gap
    from PBE (orange) and direct gap from PBE (green). The linear
    regression results are shown as broken lines.}
  \label{fig:alpha-Eg-diff}
\end{figure}

@@

\section{Theoretical Analysis}
\label{sec:theory}
\subsection{Polarizability-Based Theoretical Model}
\label{ssec:theory-1}
The universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ revealed by main text
Eqs. \ref{main-eq:2D-Moss-para} and \ref{main-eq:2D-Moss-perp} are not
coincidence. Combining recent theoretical findings of the linear
relation between exciton binding energy $E_{\mathrm{b}}$ and
$E_{\mathrm{g}}$ of 2D materials
\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
$\alpha_{\mathrm{2D}}^{\parallel}$ \cite{Pulci_2014}, it is reasonable
to have a general Moss-like relation between
$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}^{-1}$. Moreover,
the bandgap-independent relation of 2D $\alpha_{\mathrm{2D}}^{\perp}$
resembles molecular polarizabilities of conjugate molecules
\cite{Davies_1952}, fullerenes \cite{Sabirov_2014} and carbon
nanotubes \cite{Benedict_1995}, which are also shown to be
geometry-dependent.

In this section we show in detail the polarizability-based theoretical
framework that leads to the 2D Moss-like relations proposed in the
main text.  Due to its highly anisotropic nature, the wave function of
an isolated 2D material $\psi(\mathbf{r})$ can be separated into the
in- and out-of-plane components, similar to the treatment of quantum
wells (QW),\cite{davies_physics_1997} such that
$\psi^{\parallel}(\boldsymbol{\rho})$ and $\psi^{\perp}(z)$, such that
$\psi=\psi^{\parallel}\psi^{\perp}$, where $\boldsymbol{\rho}=(x, y)$
is the in-plane coordinate. Using the Bloch theorem, the periodic
$\psi^{\parallel}(\boldsymbol{\rho})$ can be further expressed as
$\psi^{\parallel}(\boldsymbol{\rho})=e^{i\mathbf{k} \cdot
  \boldsymbol{\rho}}u(\boldsymbol{\rho})$, where $\mathbf{k}$ is the
in-plane wave vector and $u(\boldsymbol{\rho})$ is periodic function
in the xy-plane. According to the random phase approximation (RPA)
theory\cite{Adler_1962}, $\varepsilon_{\mathrm{SL}}$ is the
$\mathbf{q} \to 0$ and $\omega \to 0$ limits of the non-interacting
dielectric function $\varepsilon(\mathbf{q}, \omega)$, where
$\mathbf{q}$ is the momentum transfer and $\omega$ is the frequency:
\begin{equation}
  \label{eq:RPA-eps2}
  \varepsilon_{\mathrm{SL}}
  = \lim_{\mathbf{q} \to 0} 1 + \frac{2e^{2}}{\varepsilon_{0} |\mathbf{q}|^{2} \Omega}
  \sum_{\mathrm{k, c, v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
  \left[f(\psi_{\mathrm{c}}) - f(\psi_{\mathrm{v}})\right]
\end{equation}
where $e$ is the unit charge, c, v are the conduction and valence
bands, $E$ is the eigenenergy of individual bands, and $f$ is the
Fermi-Dirac distribution function. Taking the
limit that $L\to\infty$, when
$\varepsilon^{\perp}_{\mathrm{SL}} \approx 1$, we have
$1-1/\varepsilon^{\perp}_{\mathrm{SL}} \approx
(\varepsilon_{\mathrm{SL}}^{\perp} - 1)$. Therefore
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
at 0 K can be unified by the same equation:
\begin{equation}
  \label{eq:alpha-RPA}
  \alpha = \frac{2e^{2}}{|q|^{2}A} \sum_{\mathrm{k,c,v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
\end{equation}
where the direction is determined by $\mathbf{q}$. Next we will show
that the different behavior of $\psi^{\parallel}$ and $\psi^{\perp}$
give rise to the main text Eqs. \ref{main-eq:2D-Moss-para} and
\ref{main-eq:2D-Moss-perp}.

\subsubsection{Detailed derivations for main text Eq. \ref{main-eq:2D-Moss-para}}
\label{sssec:theory-1}

>>>>

%\usepackage{xr}
%\externaldocument{paper_v112818}

\usepackage{xr-hyper} 
%\usepackage{xr}
\externaldocument{paper_v120918fundamental}

@@

\title{Electric polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
%\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
\begin{document}

\newpage{}
%\section{Further Analysis of the 2D Polarizability Model}
%\label{sec:2D-pol}

%In this section, we discuss further topics about the 2D polarizability
%model proposed in the main text.

%\section{Profile of induced dipoles of 2D material}
%\label{sec:dipole-plot}
%Here we show in detail the
%$\Delta \rho=\rho(\boldsymbol{E}) - \rho(\boldsymbol{E}=0)$ profile of
%the 2H-MoS$_{2}$ slab in main text Figure 1a. The
%density $\rho$ is calculated as the average value in the
%\textit{xy}-plane, and the value is shown in Figure
%\ref{fig:rho-profile}. As can be seen the induced charges on the
%MoS$_{2}$ layer only extends to a width of $\sim{}$12 \AA{}. When the
%SL size $L \gg$12 \AA{} as in the first principle calculations done in
%the main text, the induced dipoles from the periodic images do not
%interact, and thus giving converged values of $\alpha_{\mathrm{2D}}$.
%
%\begin{figure}[htbp]
%  \centering
%  \includegraphics[width=0.95\linewidth]{img/SI-dipole-MoS2.pdf}
%  \caption{Induced dipole profile of a 2H-MoS$_{2}$ slab inside the
%    superlattice, corresponding to main text Figure
%    \ref{main-fig-1}a. \textbf{a}. Scheme of the MoS$_{2}$ layer
%    inside the SL separated by vacuum layer. The dielectric constant
%    $\varepsilon_{\mathrm{SL}}$ is combined effect of the 2D
%    polarizability $\alpha_{\mathrm{2D}}$ and the vacuum
%    layer. \textbf{b}. $\Delta \rho$ as a function of $z$ around the
%    MoS$_{2}$ layer, green and red parts corresponding to negative and
%    positive induced charges. The external electric field
%    $E_{\mathrm{ext}}$ is 0.01 eV/\AA{}.}
%  \label{fig:rho-profile}
%\end{figure}

\section{Table of Contents}

1. Supplementary Figure \ref{fig:S1}:  Simulations of $\varepsilon_{\mathrm{SL}}$ using many-body $G_{\rm 0}W_{\rm 0}$   \\
%
%2. Supplementary Section \ref{epsilon-model}: $\varepsilon^{\parallel, \perp}_{\mathrm{SL}}$ dependence on $L$ \\ 
%
2. Supplementary Section \ref{sec:2D-3D-rescale}: Hypothetical 2D ``dielectric constant'' rescaled from 3D dielectric constant \\
%
3. Supplementary Section \ref{ssec:theory-1}: Polarizability-Based Theoretical Model  \\ 
%
4. Supplementary Section \ref{sec:pol-2D-Eg}: Dependence of $\alpha_{\mathrm{2D}}$ on bandgap \\ 
%
5.

\pagebreak{}

\section{Calculations using many-body Green function method and frequency-dependent quantities $\alpha_{\mathrm{2D}}(\omega)$ and $\varepsilon_{\mathrm{SL}}(\omega)$}

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/Fig-G0W0.pdf}
  \caption{Variation of $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
$\varepsilon^{\perp}_{\mathrm{SL}}$ as a function of $L$ for monolayer BN 
calculated at the level of PBE and G$_{\rm 0}$W$_{0}$.  
}
  \label{fig:S1}
\end{figure}

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/Fig-GW-frequency.pdf}
  \caption{Dependence of Im $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ and
Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ on $L$ for monolayer BN calculated using 
many-body G$_{\rm 0}$W$_{0}$ technique. The same {\bf k}-sampling is used in all simulations 
with the only variable quantity being $L$. The systematic shift 
}
  \label{fig:S2}
\end{figure}

\begin{figure}[htbp]
  \centering
 %\includegraphics[width=0.9\linewidth]{img/Fig-GW-frequency.pdf}
  \caption{Similar as in Fig. \ref{fig:S2} but taking into account electron-hole interactions at the level of 
  the Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE). 
  The shift in energies are reduced in comparison with G$_{\rm 0}$W$_{0}$, HSE06 and PBE but still present. 
  The magnitudes of Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega \to 0)$ varies inherently with $L$.  
}
  \label{fig:S3}
\end{figure}

%\section{$\varepsilon^{\parallel, \perp}_{\mathrm{SL}}$ dependence on $L$}
%\label{epsilon-model}
%
%Under an external electric field $\boldsymbol{E}$ the material forming the layer 
%polarizes with a polarization $\mathcal{P}_{2D}=\chi_{2D}  \boldsymbol{E} $, where  
%$\chi_{2D} $ is the electric susceptibility of the sheet. $\mathcal{P}_{2D}$ corresponds to a dipole moment 
%in the 2D material 
%of: 
%
%\begin{equation}
%\label{P_2D}
%\boldsymbol{u}_{2D}= \mathcal{P}_{2D} \Omega = (\chi_{2D}  \boldsymbol{E}) (A L)
%\end{equation}
%\\
%From Eq. \ref{P_2D} we can calculate the dipole moment density  $\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$

\pagebreak{}
\section{Hypothetical 2D ``dielectric constant'' rescaled from 3D dielectric constant}
\label{sec:2D-3D-rescale}
From literatures, it is often desired to extract the ``dielectric
constant'' of a 2D material from the 3D macroscopic dielectric
constant of the superlattice, where the layers are periodic along of
x,y directions but separated by a vacuum layer between its images
\cite{Matthes_2016,Laturia_2018}. As discussed in the main text, the
definition of the 2D ``dielectric constant'' (in particular, its
in-plane components) is questionable, due to the locality of
electrostatic screening of the 2D materials
\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Here we show
that, in addition to the ambiguous definition of the 2D dielectric
constant, such approach requires the precise determination of the 2D
layer thickness $\delta_{\mathrm{2D}}$, which makes it impractical.

@@

\begin{eqnarray}
  \label{eq:MG-effect-1}
  &\varepsilon_{\mathrm{SL}}^{\parallel} &= f \varepsilon_{\mathrm{2D}}^{\parallel} + (1 - f)\\
  \label{eq:MG-effect-2}
  &(\varepsilon_{\mathrm{SL}}^{\perp})^{-1} &= f /\varepsilon_{\mathrm{2D}}^{\perp} + (1-f)
\end{eqnarray}
where $f=\delta/L$ is the volume fraction of the 2D
material in the superlattice and $\varepsilon_{\mathrm{2D}}^{\parallel}$ and 
$\varepsilon_{\mathrm{2D}}^{\perp}$ are the corresponding dielectric constants for the 2D layer. 
The major issue when using such rescale
relations comes from the determination of $\delta_{\mathrm{2D}}$. To
eliminate the modeling error caused by the \textit{a priori} parameter
selection of $\delta$, we perform the calculation of
$\varepsilon_{\mathrm{SL}}$ of group 6 TMDCs against different $L$,
and use least-square fitting to extract both
$\varepsilon$ and $\delta$, as shown in
Figure \ref{fig:rescale-prb}.

@@

%%%%%%\section{Theoretical Analysis}
%%%%%%\label{sec:theory}
\section{Polarizability-Based Theoretical Model}
\label{ssec:theory-1}
The universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ revealed by main text
Eqs. \ref{main-eq:2D-Moss-para} and \ref{main-eq:2D-Moss-perp} are not
coincidence. Combining recent theoretical findings of the linear
relation between exciton binding energy $E_{\mathrm{b}}$ and
$E_{\mathrm{g}}$ of 2D materials
\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
$\alpha_{\mathrm{2D}}^{\parallel}$ \cite{Pulci_2014}, it is reasonable
to have a general Moss-like relation between
$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}^{-1}$. Moreover,
the bandgap-independent relation of 2D $\alpha_{\mathrm{2D}}^{\perp}$
resembles molecular polarizabilities of conjugate molecules
\cite{Davies_1952}, fullerenes \cite{Sabirov_2014} and carbon
nanotubes \cite{Benedict_1995}, which are also shown to be
geometry-dependent.

In this section we show in detail the polarizability-based theoretical
framework that leads to the 2D Moss-like relations proposed in the
main text.  Due to its highly anisotropic nature, the wave function of
an isolated 2D material $\psi(\mathbf{r})$ can be separated into the
in- and out-of-plane components, similar to the treatment of quantum
wells (QW),\cite{davies_physics_1997} such that
$\psi^{\parallel}(\boldsymbol{\rho})$ and $\psi^{\perp}(z)$, such that
$\psi=\psi^{\parallel}\psi^{\perp}$, where $\boldsymbol{\rho}=(x, y)$
is the in-plane coordinate. Using the Bloch theorem, the periodic
$\psi^{\parallel}(\boldsymbol{\rho})$ can be further expressed as
$\psi^{\parallel}(\boldsymbol{\rho})=e^{i\mathbf{k} \cdot
  \boldsymbol{\rho}}u(\boldsymbol{\rho})$, where $\mathbf{k}$ is the
in-plane wave vector and $u(\boldsymbol{\rho})$ is periodic function
in the xy-plane. According to the random phase approximation (RPA)
theory\cite{Adler_1962}, $\varepsilon_{\mathrm{SL}}$ is the
$\mathbf{q} \to 0$ and $\omega \to 0$ limits of the non-interacting
dielectric function $\varepsilon(\mathbf{q}, \omega)$, where
$\mathbf{q}$ is the momentum transfer and $\omega$ is the frequency:
\begin{equation}
  \label{eq:RPA-eps2}
  \varepsilon_{\mathrm{SL}}
  = \lim_{\mathbf{q} \to 0} 1 + \frac{2e^{2}}{\varepsilon_{0} |\mathbf{q}|^{2} \Omega}
  \sum_{\mathrm{k, c, v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
  \left[f(\psi_{\mathrm{c}}) - f(\psi_{\mathrm{v}})\right]
\end{equation}
where $e$ is the unit charge, c, v are the conduction and valence
bands, $E$ is the eigenenergy of individual bands, and $f$ is the
Fermi-Dirac distribution function. Taking the
limit that $L\to\infty$, when
$\varepsilon^{\perp}_{\mathrm{SL}} \approx 1$, we have
$1-1/\varepsilon^{\perp}_{\mathrm{SL}} \approx
(\varepsilon_{\mathrm{SL}}^{\perp} - 1)$. Therefore
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
at 0 K can be unified by the same equation:
\begin{equation}
  \label{eq:alpha-RPA}
  \alpha = \frac{2e^{2}}{|q|^{2}A} \sum_{\mathrm{k,c,v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
\end{equation}
where the direction is determined by $\mathbf{q}$. Next we will show
that the different behavior of $\psi^{\parallel}$ and $\psi^{\perp}$
give rise to the main text Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}.

{\bf ES:} There is something weird with the cross-referencing for the equations 3a and 3b between the main text and 
SI. They changed to 2a and 2b in the SI.

\subsection{Detailed derivations for main text Eq. \ref{eq:alpha-para-def} 3a}  %
\label{sssec:theory-1}

In this section we show how main text Eq. \ref{eq:alpha-para-def}
is derived from Eq. \ref{eq:alpha-RPA}. For the in-plane component
$\alpha_{\mathrm{2D}}^{\parallel}$, $e^{-i\mathbf{qr}}$ is independent
of $z$, therefore the integral in
$|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}$
becomes independent of $\psi^{\perp}$, due to the orthogonality
and normality. The Bloch-wave form of $\psi^{\parallel}$ ensures that
only the cell-function $u(\mathbf{k})$ contributes to the final result
of $\alpha^{\parallel}_{\mathrm{2D}}$ \cite{davies_physics_1997}, such
that:
\begin{equation}
  \label{eq:alpha_para_RPA}
  \alpha_{\mathrm{2D}}^{\parallel} = \frac{2e^{2}}
  {(2 \pi)^{2}} \int d^{2}\mathbf{k} \sum_{\mathrm{c, v}}
  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(\mathbf{k})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
\end{equation}
Present the summation of k-space into integral, and further combining
with the Bloch wave representation and the
$\mathbf{k} \cdot \mathbf{p}$ theory\cite{Jiang_2017_Eg_Eb}, we arrive
at Eq. \ref{eq:alpha-para-def}. Note that from
Ref. \citenum{Jiang_2017_Eg_Eb}, the coefficient between
$\alpha^{\parallel}_{\mathrm{2D}}$ and $E_{\mathrm{g}}$ is given by:
$\alpha_{\mathrm{2D}}^{\parallel} = N e^{2}/(2\pi E_{\mathrm{g}})$,
where $N$ is the degeneracy associated with the minimal bandgap. Such
relation predicts the linear correlation coefficient between
$(4\pi \varepsilon_{0})/\alpha^{\parallel}_{\mathrm{2D}}$ (measured in
\AA{}$^{-1}$) and $E_{\mathrm{g}}$ (measured in eV) as
$8 \pi^{2} \varepsilon_{0} \AA{} / (e N) \approx 0.436 / N$. From Figure 2{\bf c}, we have
$(4 \pi \varepsilon_{0}\cdot \text{\AA{}})/\alpha_{\mathrm{2D}}^{\parallel}
\sim{} 0.183 E_{\mathrm{g}}/ \mathrm{eV}$, corresponding to $N$
between 2 and 3, which is a reasonable result for the 2D materials
studied.

{\bf ES:} Tian, please include more details in this section on the derivations!

\subsection{Detailed derivations for main text Eq. \ref{eq:alpha-perp-def}}
\label{ssec:theory-2}

For main text Eq. \ref{eq:alpha-perp-def}, treating the in-plane
wave functions as plane wave with form
$\psi^{\parallel}(\rho) \propto e^{i \mathbf{k \rho}}$, the matrix
element of
$<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{qr}}|\psi_{\mathrm{c}}(\mathbf{k+q})>$,
when $\mathbf{q}=(0, 0, q_{z})$, becomes\cite{Hybertsen_1987}:
\begin{equation}
  \begin{aligned}
    \label{eq:matrix-z}
  <\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{qr}}|\psi_{\mathrm{c}}(\mathbf{k+q})>
  &= \frac{1}{A} \int dx \int dy
  e^{i(\mathbf{-k \rho} - \mathbf{q \rho} + \mathbf{(k+q) \rho})}
  \int (\psi^{\perp})^{*}_{\mathrm{v}}(\mathbf{k})e^{-iq_{z}z}\psi^{\perp}_{\mathrm{c}}(\mathbf{k+q})\\
  &= <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|e^{-iq_{z}z}|\psi^{\perp}_{\mathrm{c}}(\mathbf{k+q})>
  \end{aligned}
\end{equation}
Note that the states perpendicular are bound, the integral is
meaningful only when $\mathbf{k=k+q}$ \cite{davies_physics_1997}. By
performing the Taylor expansion of
$e^{-i\mathbf{qr}} \approx 1 - i\mathbf{qr}$, we get:
\begin{equation}
  \begin{aligned}
    \label{eq:matrix-z-2}
    <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|e^{-iq_{z}z}|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>
    &\approx <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})> -
    iq_{z} <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|z|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>\\
    &= -iq_{z} <\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|z|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>
   \end{aligned}
\end{equation}
plug this into Eq. \ref{eq:alpha-RPA} and express the summation over
$k_{x}$ and $k_{y}$ in a continuous form within the Brillouin Zone, we
arrive at:
\begin{equation}
\label{eq:alpha_perp_RPA}
\alpha_{\mathrm{2D}}^{\perp} = \frac{2e^{2}}{(2 \pi) ^{2}} \int d^{2}\mathbf{k}
\sum_{\mathrm{c, v}}
\frac{|<\psi_{\mathrm{v}}(\mathbf{k})|z|\psi_{\mathrm{c}}(\mathbf{k})>|^{2}}
{E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
\end{equation}
The formalism is slightly different from Eq.\ref{eq:alpha_para_RPA}.

The out-of-plane wave function $\psi^{\perp}(z)$ is the solution to the Schr\"{o}dinger equation with
Hamiltonian $\mathcal{H} = -\hbar^{2} \nabla^{2}/2m_{e} + V(z)$, where
$\hbar$ is the reduced Planck constant, $m_{e}$ is electron mass and
$V(z)$ is the confined Coulomb potential along the z-direction
created by the nuclei
\cite{davies_physics_1997,ihn_semiconductor_2009}. Although the exact
form for $\psi^{\perp}$ depends on the exact distribution of $V(z)$,
without loss of generality we can assume the electrons are confined in
a potential well of width $\delta$, which is the typical treatment for
semiconductor QWs \cite{ihn_semiconductor_2009}. The allowed bound
states inside the confined region generally have wave vector
$k_{z} \propto n \pi / \delta$. With the total energy
$E_{n}(\mathbf{k}) = {\displaystyle \frac{\hbar^{2} (k_{x}^{2} +
    k_{y}^{2})}{2 m^{\parallel}} + \frac{\hbar^{2} n^{2} \pi^{2}}{2
    m^{\perp} \delta^{2}}}$, where $m^{\parallel}$ and $m^{\perp}$ are
the effective masses parallel and perpendicular to the 2D
plane. Therefore the denominator of Eq. \ref{eq:alpha_perp_RPA} becomes independent of
$\mathbf{k}$, that
$E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k}) =
(n_{\mathrm{c}}^{2} - n_{\mathrm{v}}^{2}) {\displaystyle
  \frac{\hbar^{2} \pi^{2}}{2 m^{\perp} \delta^{2}}}$. On the other
hand, the numerator
$<\psi^{\perp}_{\mathrm{v}}(\mathbf{k})|z|\psi^{\perp}_{\mathrm{c}}(\mathbf{k})>$
is proportional to the confinement length $\delta$ which can be seen using
particle-in-box solution\cite{davies_physics_1997}. In combination,
the individual terms of the summation in the right hand of Eq. \ref{eq:alpha_perp_RPA} is
independent of neither $E_{\mathrm{g}}$ nor \textbf{k}, proving that
$\alpha_{\mathrm{2D}}^{\perp}$ is independent of the band gap.

Finally we will show the $\alpha_{\mathrm{2D}}^{\perp}$ is related to the
confinement length $\delta$, or equivalent the thickness of the 2D
material. For simplicity we assume $\psi^{\parallel}$ is the solution
of a particle confined inside an infinite potential well of width
$\delta$ with the form $\psi \propto \sin(\frac{n\pi}{\delta})$. At 0
K, the only non-zero contribution for the transition between band
$n_{\mathrm{v}}$ and $n_{\mathrm{c}}$ corresponds with in-plane wave
vector $\mathbf{k}_{\rho}$ within the range of $k_{\mathrm{F}}^{\mathrm{v}}$ to
$k_{\mathrm{F}}^{\mathrm{c}}$, the Fermi vectors of each band. Therefore we have:
\begin{equation}
  \begin{aligned}
    \alpha_{\mathrm{2D}}^{\perp} &\propto \delta^{4} m^{\perp} \int
    d^{2}\mathbf{k}_{\rho}
    \frac{f(\psi_{\mathrm{v}}(\mathbf{k}_{\rho}))
      -f(\psi_{\mathrm{v}}(\mathbf{k}_{\rho})) }{n_{\mathrm{c}}^{2} -
      n_{\mathrm{v}}^{2}}\\
    &= \delta^{4} m^{\perp} \sum_{\mathrm{c, v}}\pi \frac{
      (k_{\mathrm{F}}^{\mathrm{c}})^{2} -
        (k_{\mathrm{F}}^{\mathrm{v}})^{2}}{n_{\mathrm{c}}^{2} -
        n_{\mathrm{v}}^{2}}
  \end{aligned}
\end{equation}
Since the Fermi wave vector for band \textit{i} follows
${\displaystyle
  \frac{\hbar^{2}(k_{\mathrm{F}}^{i})^{2}}{2m^{\parallel}}} +
{\displaystyle \frac{\hbar^{2} n_{i}^{2} \pi^{2}}{2m^{\perp}
    \delta^{2}}} = E_{\mathrm{F}}$, we have
$ (k_{\mathrm{F}}^{\mathrm{c}})^{2} -
(k_{\mathrm{F}}^{\mathrm{v}})^{2} \propto (n_{\mathrm{c}}^{2} -
n_{\mathrm{v}}^{2}) {\displaystyle
  \frac{m^{\parallel}}{m^{\perp}}}$. Note that in the particle-in-box
model, the energy levels for a sub-nm QW will be at the order of 10
eV, which allows only few states inside the QW. Combine with the fact
that the strongest transition mostly comes from the lowest bands
\cite{davies_physics_1997}, $\alpha^{\perp}_{\mathrm{2D}}$ is shown to
be proportional to $\delta^{p}$, where the power index $p$ is 2. We
note the different power law comes from the choice of the $V(z)$. The
atomic polarizabilities of free particles inside a 1D infinite QW,
finite QW or harmonic QW all show dependency with $\delta^{4}$, where
$\delta$ is the length of confinement or effective harmonic length of
the QW \cite{Fowler_1984,Maize_2011}. Since the 2D polarizability is
the molecular polarizability divided by the area, such approach will
always yield $\alpha_{\mathrm{2D}}^{\perp} \propto \delta^{2}$. To
accurately model the $\alpha_{\mathrm{2D}}^{\perp}$ we need a better
model for the confinement in z-direction than simple square potential
well, which may be explored further. Nevertheless the simple model presented
here still captures the bandgap-independent and thickness-related feature
of $\alpha_{\mathrm{2D}}^{\perp}$, supporting our findings in the main
text. In the next section we will provide a simple explanation for the $\alpha \propto \delta$ relation from fundamental electrostatics theory.

\section{Dependence of $\alpha_{\mathrm{2D}}$ on bandgap}
\label{sec:pol-2D-Eg}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\linewidth]{img/SI-compare_alpha_Eg.pdf}
  \caption{Relation between $1/\alpha_{\mathrm{2D}}^{\parallel}$ and various choices
    of $E_{\mathrm{g}}$: minimal gap from HSE06 (blue), minimal gap
    from PBE (orange) and direct gap from PBE (green). The linear
    regression results are shown as broken lines.}
  \label{fig:alpha-Eg-diff}
\end{figure}

@@

%%%%%%pasted in 12/05/2018

\subsection{Explanation to main text Eq. \ref{main-eq:2D-Moss-perp}
  from fundamental electrostatics}
\label{sssec:theory-3}
